---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metawho

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ShixiangWang/metawho?branch=master&svg=true)](https://ci.appveyor.com/project/ShixiangWang/metawho) [![Travis build status](https://travis-ci.org/ShixiangWang/metawho.svg?branch=master)](https://travis-ci.org/ShixiangWang/metawho) [![Coverage status](https://codecov.io/gh/ShixiangWang/metawho/branch/master/graph/badge.svg)](https://codecov.io/github/ShixiangWang/metawho?branch=master)

The goal of **metawho** is to provide simple R implementation of "Meta-analytical method to Identify Who Benefits Most from Treatments" (called 'deft' approach, see [reference #2](#references)).

**metawho** is powered by R package **metafor** and does not support dataset contains individuals for now. Please use stata package **ipdmetan** if you are more familar with stata code.

## Installation

You can install the development version of **metawho** from GitHub with:

``` r
remotes::install_github("ShixiangWang/metawho")
```

## Example

This is a basic example which shows you how to solve a common problem.

Load example data.

```{r load_wang2019}
library(metawho)
data("wang2019")

wang2019
```

Use `deft_do()` function to obtain model results.

```{r}
# The 'Male' is the reference
(res = deft_do(wang2019, group_level = c("Male", "Female")))
```

Plot the results with `forest()` function from **metafor** package.

```{r}
forest(res$subgroup$model, showweights = TRUE)
```

Modify plot, more see `?forest.rma`.

```{r}
forest(res$subgroup$model, showweights = TRUE, atransf = exp, 
       slab = res$subgroup$data$trial,
       xlab = "Hazard ratio")
op = par(no.readonly = TRUE)
par(cex = 0.75, font = 2)
text(-11.5, 4.5, "Trial(s) and subgroup", pos = 4)
text(9, 4.5, "Hazard Risk [95% CI]", pos = 2)
par(op)
```


## References

-  Wang, Shixiang, et al. "The predictive power of tumor mutational burden in lung cancer immunotherapy response is influenced by patients' sex." International journal of cancer (2019).
- Fisher, David J., et al. "Meta-analytical methods to identify who benefits most from treatments: daft, deluded, or deft approach?." bmj 356 (2017): j573.
